### 2018-04-18 paper_wc_proof.tex
Moving PhD paper from Dropbox to github.

We begin to construct the model for a PSP data auction for  mobile users
particpating in CMHK's secondary data-sharing market.
Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
cellular network. We assume that users are selfish, and therefore
rational. 
 Users prefer to participate in the secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which typically
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We will assume that the user valuation satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}. 
As the CMHK market does not allow for brokers \cite{cmhk}, we determine that
the bid profiles must adhere to some additional restrictions, which we will
imply using the PSP bid profile notation.
A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
the bid belongs to a \textbf{seller}.
Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
(0,0)$. Naturally, in a live auction, if a buyer does
not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
and seller $j$.
A seller $j$ places an ask $s_i^j = (d_i^j, p_i^j)$, meaning $j$ is offering a
quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
by the user type, whether or not they are  a buyer or a seller. 
To further clarify our analysis, we will emphasize the separation of buyers and
sellers using
$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
In other words, a bid $s^j =
[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
secondary market. The notational conventions of the bid vectors are essentially 
slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
d_i^j$ represent the
total amount of data requested by buyer $i$. 
Finally, we assume that data is a unary resource belonging to the seller, and
therefore can identify each local auction
with the identity of the seller $j\in\mcI$.

Consider the grid of bid proiles, $s$, representing the distributed PSP auction
mechanism in the CMHK market, each buyer $i$ will
have information from each seller $j$, as well as opponent profiles $s_{-i}$
from each auction in which it is participating, and therefore
in the extreme case, buyer $i$ gains access to the full grid $s$. The extreme with respect to
$i$ is the case where buyer $i$ will participates in all auctions $j\in\mcI$
(SHOULD I PROVE THIS OR TOO TRIVIAL?). However, 
sellers can only gain information about the market grid by observing buyer
behavior in their local auction.
In our current formulation, we do not allow a seller to host multiple
auctions(FUTURE WORK?). Thus, only the buyers are able to directly and globally
influence the CMHK market dynamics, with the sellers taking a secondary role
(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).

@@

We are not concerned with network
bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, however
we reason that there remains an optimal user strategy. As a user no longer needs
to bid on a complete (but arbitrary)
cluster of nodes with minimum bandwidth allocation (defined as a route in
\cite{semret}), we reason that a buyer may opt-out of auctions, maximizing its
utility while minimizing the number of positive bids submitted to the overall
market. We define an \textbf{opt-out function}, $e$, as a function that when composed with our user type to describes
its market behavior. In a general sense, $e$ applies our user \emph{strategy}
to the PSP rules.
Our reserve price function is determined by the subset of nodes participating in the
auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the market via the $\epsilon$-best replies from the
buyers. We demonstrate that as the valuation function of seller $j$ is dependent
on the buyers demand, and further show evidence of symmetry in the strategies of
buyers and sellers.

@@

% USER UNION
{
\lemma{(Valuation across local auctions)}\label{userunion}
For any $i,j\in \mcI$, 
\begin{equation}\label{jtoi}
j\in\mcI_i \Leftrightarrow i\in\mcI^j.
\end{equation}
Fix an auction $j\in\mcI$ and define the set of users $\Lambda$, where
\begin{equation}\label{lambda}
    \lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
\end{equation}
\begin{equation}\label{lambda}
    \Lambda = \bigcap_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg),
\end{equation}
\begin{equation}\label{lambda}
    \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
\end{equation}
and for each $i\in\mcI^j$ define,
\begin{equation}\label{ilambda}
    \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
\bigg).
\end{equation}
(WANT TO SAY $s_i^j > 0$ iff $i,j \in\Lambda \Rightarrow s_i^j \in \Lambda
\equiv s_i^j \in \mcI$)
Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$,
\begin{equation}\label{sym}
    (\theta_i \circ \theta^j) = (\theta^j \circ \theta_i).
\end{equation}
(ONLY HAVE ONE HALF OF THE SYMMETRY SO FAR! REALLY WANT TO MAKE $s_i = s^j$
HAPPEN)
}\\
\textbf{Proof:}
A local auction $j\in\mcI$, is determined by the collection of buyer bid
profiles, where $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
if and only if $p_i^j \ge p_{i^*}^j$.
Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
If $i^* \ni \mcI^j$, then (\ref{jtoi}) holds; in the latter case, by
Proposition \ref{buyerstrategy}, $i^*$
will add sellers to its pool until its demand is satisfied. Therefore for any
$j\in\mcI_i$, $\not\exists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
holds.

The subset $\mcI^j \subset \mcI$
determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
coordinated, truthful bid, $\mcI_i\subset \mcI$ 
will determine the unit price $p_{i}$ in buyer $i$'s bid.
(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
price, which in turn defines $j$'s reserve price, $p_{i^*}^j$,
the lowest price that $j$ will accept to perform any allocation.
Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
\ref{sellerstrategy},
we have that for each $i \in \mcI^j$, 
$p_{i}^j \ge p_{i^*}^j \ge p_i^k > 0$, which holds $\forall \ k \in\mcI_i$.
Let $p_*^j=p_{i^*}^j$ denote the reserve
price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
[p_i^j]_{i\ni\mcI^j}$.
Now, we have,
%Fix any buyer $i\in\mcI^j$.
\begin{equation}\label{rho}
    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
\end{equation}
and, $\forall \ i \in \mcI^j$, 
\begin{equation}\label{invrho}
    f_i \circ e_i^j(a) \ge p_*^j,
\end{equation}
and, $\forall \ k \in \mcI_i$, 
\begin{equation}\label{invrho}
    p_*^j \ge f^k \circ e_i^k(a) ,
\end{equation}
from (\ref{datademand}), (\ref{buyerinversedemand}),
(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$

The sellers $\in\Lambda$ are competing to sell
their respective resources to buyers whose valuations are distributed across multiple auctions. 
%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
Consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0$
for any $k\ne j \in \mcI_i$. 
Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we have
$\forall \ i \in \mcI^j$,
\begin{equation}\label{feq}
    p_*^j = f^j \circ e_i(a) = f_i\circ e_i(a) = p_i^*,
\end{equation}
where we denote $p_i^*$ as the coordinated bid price of buyer $i$.
Now, suppose $\exists \ i\in\mcI^j$ such that $p_i^* \ge p_*^j$.
Since,
$$
    p_i^* = \max_{k\in\Lambda_i}(f^k) \circ e_i(a)= \max_{k\in\Lambda_i}(p_*^k),
$$ 
there must be some $k \ \in\mcI_{i}$, where $p_i^k > p_*^j$, and so, 
we have that $ \Rightarrow p_i^k > p_*^j$. Also, $\not\exists$(HERE) 
It follows that buyer $i$'s bid price is given by,
\begin{equation}\label{iprice}
    p_i^j = \max_{j\in\Lambda}(f^j) \circ e_i(a)= \max_{j\in\Lambda}(p_*^j),
\end{equation}

%where $p_i^*$ represents $i$'s coordinated bid price,
%i.e., $p_i^j = p_i^*, \ \forall \ j$ such that $s_i^j > 0$.
This holds for any
$i\in\mcI^j$ and similarly if $p_i^k < p_i^j$. 
Now, from (\ref{feq}), we have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, as such, we may
denote each as $f$ in the remainder of the proof.

Now, using (\ref{rho}), and intersection of subspaces, we determine the aggregate demand from buyer
$i\in\mcI^j$ to be, (HERE)
(SHOW THAT $\Lambda$ IS DISJOINT!)
\begin{equation}\label{sumrho}
    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p_*^k) =
\sum_{k\in\mcI_i\cup\mcI^j}
e_i^k(a),
\end{equation}
where $p^k$ is the highest unit price in the feasible set $\mcI_i\cup\mcI_k$.
Thus we determine the aggregate demand from buyer
$i\in\mcI^j$ over the set of intersecting markets $\Lambda$ to be, 
\begin{equation}\label{sumrho}
    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p^*) =
\sum_{k\in\mcI_i\cup\mcI^j}
e_i^k(a),
\end{equation}
where $p^* = \max(p^k), \ \forall \ k \in\Lambda$, and corresponds to the
highest reserve price over all the sellers. 
Now, by the continuity of $\theta'$, (AND)
\begin{align*}
     \displaystyle\sum_{i\in\mcI^j} &\bigg(\sum_{k\in\mcI_i\cup\mcI^j}\int_0^{e_i^k(a)}
f(z) \ dz\bigg)\\
     &=\displaystyle\sum_{i\in\mcI^j} \theta_i \circ e_i(a) \\
     &= \sum_{k\in\mcI_i\cup\mcI^j}\bigg(\sum_{i\in\mcI^j}\int_0^{e_i^k(a)}
f(z) \ dz\bigg)\\
     &= \sum_{k\in\mcI_i\cup\mcI^j}\theta^j \circ e_i(a)\\
     &= (\theta_i \circ \theta^j) \circ e_i(a).
\end{align*}

\iffalse
************************
Proposition \ref{buyerstrategy} defines $e_i^j(a) = D_i/ 2$, and so $0 <
e_i^j(a)$.
************************
\fi
\iffalse
Suppose $\exists \ i \in\mcI^j$ such that $\mcI_i = j$, so that $j$ is the only
seller in $\Lambda$.
, and $i$'s bid quantity,
\begin{equation}\label{iquantity}
    d_i^* = \circ e_i(a) = \frac{a_i^j}{j},
\end{equation}
where $j=j^* = \argmin$ for each $i\in\mcI^j$, thus $d_i^*$ represents $i$'s coordinated bid quantity, and we have
$s_i^j = (p_i^*,d_i^*), \ \forall \ j$ such that $s_i^j > 0$,
\fi
\iffalse

*****************************************************************************************************
From (\ref{jtoi}), $i\in\mcI^j \Rightarrow
j\in \mcI_i$, so $i\in \mcI^j \cup \mcI^j$, 
Using (\ref{buyerinversedemand}), we have the valuation of $j\in\mcI_i$,
%$i\in\bigcap_{i\in\mcI^j}\mcI_i$,
\begin{align*}
      \theta^j \circ e = \sum_{k\in\mcI_i\cup\mcI^j}}&\int_0^{e_i^k(a)} f(z) \ dz,
\end{align*}
and by (\ref{sellerinversedemand}), we have the valuation of $j$ fixed, 
\begin{align*}
      \theta^j \circ e = \sum_{i\in\mcI^j}&\int_0^{e_i^j(a)} f(z) \ dz,
\end{align*}
and thus we have the valuation of $\Lambda^j$,
\begin{align*}
     \displaystyle\sum_{i\in\mcI^j} \bigg(\sum_{k\in\Lambda}&\int_0^{e_i^k(a)}
f(z) \ dz\bigg).
\end{align*}
\\(FINISH!)\\
$$
     \displaystyle\sum_{j\in\mcI_i} \bigg(\sum_{k\in\Lambda}\int_0^{e_k^j(a)}
f(z) \ dz\bigg).
$$
----------------HERE--------------\\
(HOW TO MAKE SETS THE SAME???)
Now we consider $\Lambda_i$. For each buyer $i\in\mcI^j$, we have that $p_i^j
\ge p_i^k$

Now, for $\Lambda_i \cap \Lambda^j$, and by the continuity of $\theta'$,
\begin{align*}
     \displaystyle\sum_{i\in\mcI^j} &\bigg(\sum_{k\in\Lambda_i}\int_0^{e_i^k(a)}
f(z) \ dz\bigg)\\
     &= \sum_{k\in\Lambda_i}\bigg(\sum_{i\in\mcI^j}\int_0^{e_i^k(a)}
f(z) \ dz\bigg)\\
      &= \sum_{k\in\Lambda^j}\bigg(\sum_{j\in\mcI_i}\int_0^{e_k^j(a)}
f(z) \ dz\bigg)\\
      &=\sum_{j\in\mcI_i} \bigg(\sum_{k\in\Lambda^j}\int_0^{e_k^j(a)}
f(z) \ dz\bigg).
\end{align*}

(WHAT?)\\
Therefore, $\Lambda$ is such that $j\ni \mcI_i, \ \forall \ i \ni \mcI^j$. In other words, $\Lambda$ is a
disjoint set in the global marketplace with respect to $j$.
****************************************************************************************************
\fi

For completeness, in the case where the ISP $\kappa$ 
does not adhere to the market dynamics, so $P^\kappa > p^j +
\epsilon, \ \forall \ j \in\mcI$, then we may absorb the overage (difference) as part of the
bid fee.

>>>>

We begin to construct the model for a PSP data auction for  mobile users
particpating in CMHK's secondary data-sharing market.
Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
cellular network. We assume that users are selfish, and therefore
rational. 
 Users prefer to participate in the secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which typically
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We will assume that the user valuation satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}. 
As the CMHK market does not allow for brokers \cite{cmhk}, we determine that
the bid profiles must adhere to some additional restrictions, which we will
imply using the PSP bid profile notation.
A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
the bid belongs to a \textbf{seller}.
Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
(0,0)$. Naturally, in a live auction, if a buyer does
not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
and seller $j$.
A seller $j$ places an ask $s_i^j = (d_i^j, p_i^j)$, meaning $j$ is offering a
quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
by the user type, whether or not they are  a buyer or a seller. 
To further clarify our analysis, we will emphasize the separation of buyers and
sellers using
$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
In other words, a bid $s^j =
[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
secondary market. The notational conventions of the bid vectors are essentially 
slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
d_i^j$ represent the
total amount of data requested by buyer $i$. 
Finally, we assume that data is a unary resource belonging to the seller, and
therefore we identify each local auction
with the identity of the seller $j\in\mcI$.

Consider the grid of bid proiles, $s$, representing the distributed PSP auction
mechanism in the CMHK market, each buyer $i$ will
have information from each seller $j$, as well as opponent profiles $s_{-i}$
from each auction in which it is participating, and therefore
in the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
$i$ gains access to the full grid $s$. However, 
sellers can only gain information about the market grid by observing buyer
behavior in their local auction.
In our current formulation, we do not allow a seller to host multiple
auctions(FUTURE WORK?). Thus, only the buyers are able to directly and globally
influence the CMHK market dynamics, with the sellers taking a secondary role
(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).

@@

We are not concerned with network
bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, however
we reason that there remains an optimal user strategy suited for the
data-sharing model. As a user no longer needs
to bid on a complete (but arbitrary)
cluster of nodes with minimum bandwidth allocation (defined as a route in
\cite{semret}), we reason that a buyer may opt-out of auctions, maximizing its
utility while minimizing the number of positive bids submitted to the overall
market. We define an \textbf{opt-out function}, $e$, as a function that when composed with our user type to describes
its market behavior. In a general sense, $e$ applies our user \emph{strategy}
to the PSP rules.
Our reserve price function is determined by the subset of nodes participating in the
auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the market via the $\epsilon$-best replies from the
buyers. We demonstrate that as the valuation function of seller $j$ is dependent
on the buyers demand, and further show evidence of symmetry in the strategies of
buyers and sellers.

@@

% USER UNION
{
\lemma{(Valuation across local auctions)}\label{userunion}
For any $i,j\in \mcI$, 
\begin{equation}\label{jtoi}
j\in\mcI_i \Leftrightarrow i\in\mcI^j.
\end{equation}
Fix an auction $j\in\mcI$ and define the influence sets of users. 
The primary influencing set is given as,
(ALL THE SELLERS FROM EACH BUYERS POOL)
\begin{equation}\label{lambda}
    \Lambda = \displaystyle\bigcup_{i\in\mcI^j} \mcI_i,
\end{equation}
with secondary influencing set,
(ALL THE BUYERS FROM EACH SELLER $i$ IN $j$'s BUYER POOL)
\begin{equation}\label{llambda}
    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcup_{k\in\mcI_i} \mcI^k \bigg)
\end{equation}
(THE SELLERS ALL THE BUYERS IN $j$ HAVE IN COMMON! i.e. $j$ AND...)
\begin{equation}%\label{lambda}
    \Lambda = \displaystyle\bigcap_{i\in\mcI^j} \mcI_i,
\end{equation}
(THE COLLECTION OF BUYERS FROM EACH $i$ THAT ARE COMMON ACROSS ALL THE $i$'s SELLER
POOLS)
\begin{equation}%\label{llambda}
    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg)
\end{equation}
\iffalse 
***********************************
\begin{equation}
    \Lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
\end{equation}
\begin{equation}
    \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
\end{equation}
and for each $i\in\mcI^j$ define,
\begin{equation}
    \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
\bigg).
\end{equation}
we have $\forall \ i \in
\mcI^j$,
\begin{equation}\label{sym}
    (\theta_i \circ \theta^j) = (\theta^j \circ \theta_i).
\end{equation}

***********************************
\fi
Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$, (ONLY HAVE ONE HALF OF THE SYMMETRY SO FAR! REALLY WANT TO MAKE $s_i = s^j$
HAPPEN)
}\\
\textbf{Proof:}
A local auction $j\in\mcI$, is determined by the collection of buyer bid
profiles, where $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
if and only if $i$'s bid is such that $p_i^j \ge p_{i^*}^j$, where
(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
price in auction $j$.
Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
If $i^* \ni \mcI^j$, then (\ref{jtoi}) holds; in the latter case, by
Proposition \ref{buyerstrategy}, $i^*$
will add sellers to its pool until its demand is satisfied. Therefore for any
$j\in\mcI_i$, $\nexists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
holds.
Furthermore, we note that $\lambda \subset \mcI$ is a complete and disjoint set
of bid vectors with respect to auction $j$. That is, $\forall \ i \in \mcI^j,
s_i^k > 0 \in \lambda$ if and only if $s_i^k>0 \in\mcI$, and so $s_i \in \lambda
\equiv s_i \in \mcI$. (NEED TO ADD TO LEMMA AND PROVE?)

Now, the subset $\mcI^j \subset \mcI$
determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
coordinated, truthful bid, $\mcI_i\subset \mcI$ 
will determine the unit price $p_{i}$ in buyer $i$'s bid.
The reserve price (\ref{newprice}) of seller $j$ is determined at time $t$, and is
the lowest price that $j$ will accept to perform any allocation.
Let $p_*^j = f^j \circ e_i^j(a) $ denote the reserve
price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
[p_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ e_i^j(a)$ the (coordinated) bid price of buyer $i$, i.e. $p_i^k = p_i^*,
\ \forall \ k \in\mcI_i$. 
Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
\ref{sellerstrategy}, $\forall \ i \in \mcI^j$, we have that $p_i^* \ge p_*^k,
\ \forall \ k \in\mcI_i$.

\iffalse
Now, we have,
\begin{equation}\label{rho}
    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
\end{equation}
from (\ref{datademand}), (\ref{buyerinversedemand}),
(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
\fi

The incentive of each seller $\in\Lambda$ is to sell all of its data at the
best possible price. In the simplest case,
consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0,
\ \forall \ k\ne j \in \mcI_i \Rightarrow \Lambda = \lbrace j \rbrace$ and
$\lambda = \mcI^j$. 
Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we clearly
have that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
In all other cases, the sellers $\in\Lambda$ are competing to sell
their respective resources to buyers whose valuations are distributed across multiple auctions. 
%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
The set $\lambda$ represents all of the buyers influencing auction $j$, both
directly and indirectly. 
The bid price of buyer $i\in\mcI^j$ is determined by,
\begin{equation}\label{maxbid}
    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ e_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
\end{equation}
$\Lambda$ is the set of sellers that directly influence the bids of buyers
$\in\mcI^j$. the reserve price for auction $j$ is such that,
\begin{equation}\label{resprice}
    p_*^j \le \min_{i\in\mcI^j}(p_i^*) - \epsilon,
\end{equation}
by Proposition \ref{sellerstrategy}.

We have from Proposition \ref{sellerstrategy} that $j$ maintains a local market
equilibrium at time $t$. Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
and suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
that $p_*^q > p_*^j$. Then, a change in $q$'s valuation from time $t$ to $t+1$ will
directly impact seller $j$. If at time $t+1$ we still have that $i$ is the
buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and
thus $j$'s valuation does not change. Otherwise a new buyer with the lowest bid will be chosen upon
recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}. 
In each case we
have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
fixed time $t$, and so, $\forall \ i \in\mcI^j$,
\begin{align*}
    \int_0^{e_i^j(a)} f^j(z) \ dz &= \theta_i^j \circ e_i^j(a)\\
    &= \int_0^{e_i^j(a)} f_i(z) \ dz,
\end{align*}
therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
Furthermore, using (\ref{datademand}), it follows that,
\begin{equation}\label{jdemand}
    \displaystyle\sum_{i\in\mcI^j}\int_0^{e_i^j(a)} f_i(z) \ dz = \int_0^{D^j}
f^j(z) \ dz.
\end{equation}

Consider the set $\lambda$. For some buyer $i\in\mcI^j$, and then for
some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
that $p_l^* < p_*^j$. We have that
the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, and so we must
have that $p_l^* < p_i^*$,
and necessarily, $p_i^* > p_l^*$ for
any buyer $l\in\lambda$ such that $l\ni \mcI^j$. 
Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$. % \Rightarrow \theta_l^q > \theta_l^k$. 
Again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
\ni\mcI^q \Rightarrow p_*^q >
p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
buyer $i$. 
Lastly, 
in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q = 0$.
We have that for any $l\in\mcI^k$ such that $l\ni
\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$
for $q\in\mcI_l$ or $\theta_l^q = 0$ for $q\in\mcI_i$. Thus, any bid ouside of
our construction
has a zero valuation, with respect to buyers $\in\lambda$ and sellers
$\in\Lambda$. We have,
\begin{equation}\label{idemand}
    \displaystyle\int_0^{D_i} f_i(z) \ dz = \sum_{k\in\mcI_i}\int_0^{e_i^k(a)}
f_i(z) \ dz,
\end{equation}
\begin{align*}
  \int_0^{D^j} f^j(z) \ dz = \displaystyle\sum_{i\in\mcI^j}\int_0^{e_i^j(a)} f^j(z) \ dz = \int_0^{e_l^k(a)} f^k(z) \ dz.
\end{align*}
Thus, by construction, 
\iffalse
\begin{align*}
    \displaystyle\sum_{i\in\mcI^j} &\bigg( \sum_{k\in\mcI_i} \int_0^{e_i^k(a)}
f^k(z) \ dz \bigg) \\
    &= \sum_{i\in\mcI^j}\bigg(\sum_{k\in\mcI_i}\bigg(\sum_{l\in\mcI^k}\int_0^{e_l^k(a)} f^k(z) \ dz.
\bigg)\bigg)
\end{align*}
\fi
the continuity of $\theta$, and using (\ref{jdemand}), (\ref{idemand}),
\begin{align*}
    \int_0^{e_i^k(a)} f_i(z) \ dz &= \int_0^{e_i^k(a)} f^k(z) \ dz \\
    = \int_0^{e_l^k(a)} f^k(z) \ dz &= \int_0^{e_l^k(a)} f_l(z) \ dz \\
\end{align*}
Finally, we have,
\begin{equation}
    \displaystyle\sum_{j\in\Lambda} \int_0^{e_i^j(a)} f_i(z) \ dz = \sum_{i\in\lambda}\int_0^{D^j} f^j(z) \ dz.
\end{equation}

\vspace{3cm}
(KEEP GOING! YOU ARE DOING GREAT!)\\
For completeness, in the case where the ISP $\kappa$ 
does not adhere to the market dynamics, so $P^\kappa > p^j +
\epsilon, \ \forall \ j \in\mcI$, then we may absorb the overage (difference) as part of the
bid fee.
